---
title: "R Notebook"
output: html_notebook
---

# plot model estimates

```{r}
library(tidyverse)
library(ggseg)
library(ggplot2)
library(corrplot)
library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)
library(sjPlot)  # For extracting confidence intervals
library(ggeffects)

```

#encoding

## data to load
```{r}
results <- read_csv("viewing_slopes_April2026.csv")
```

## plot
```{r}
roi_list <-c('PMC',
             'dmPFC',
             'ATL',
             'vmPFC',
             'MTL',
             'PreC',
             'vLP',
             'dLP',
             'aLP',
             'SMC')

colors <- c("#63aff9","#ff0000","#ff7700","#f5c042","#2c9741","#8adA99","#003300","#3c1d8a","#a61712","#60ebeb")
p<-ggplot(results,aes( y = term_beta, x = fct_relevel(file,"vmPFC","PMC","dLP","aLP","dmPFC","ATL","MTL","PreC", "vLP", "SMC"), color = file)) +
  geom_point(size =5) +
  geom_errorbar(aes(ymin =term_beta-term_se, ymax = term_beta+term_se), width = 0,linewidth=2) +
  geom_hline(yintercept = 0, linetype ="dashed", color = "gray40") +
  theme_minimal() +
  ylim(-0.003, .014)+
  scale_color_manual(values =setNames(colors, results$file))+
  labs(title = "Encoding ISPS",size = 40)+
  theme(
    plot.title=element_text(size = 30, hjust =0.5),
    plot.margin = unit(c(1,.5,.5,.5),"cm"),
    panel.grid.major.x = element_blank(),
    #panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    axis.title.y = element_text(size = 30),
    axis.title.x = element_blank(),
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black"),
    axis.text = element_text(size = 25),
    axis.text.x = element_text(angle=90,size = 18),
    legend.position = "none") +
    ylab("Model Estimate")
  
  

ggsave('encodingISPS_topicSim_estimates_v6.png', width = 4.5,height = 6, units = "in", dpi = 300)

```

# recall

## data to load
```{r}
results <- read_csv("recall_slopes_April2026.csv")
```


## plot
```{r}
roi_list <-c('PMC',
             'dmPFC',
             'ATL',
             'vmPFC',
             'MTL',
             'PreC',
             'vLP',
             'dLP',
             'aLP',
             'SMC')

colors <- c("#63aff9","#ff0000","#ff7700","#f5c042","#2c9741","#8adA99","#003300","#3c1d8a","#a61712","#60ebeb")
p<-ggplot(results,aes( y = term_beta, x = fct_relevel(file,"vmPFC","PMC","dLP","aLP","dmPFC","ATL","MTL","PreC", "vLP", "SMC"), color = file)) +
  geom_point(size =5) +
  geom_errorbar(aes(ymin =term_beta-term_se, ymax = term_beta+term_se), width = 0,linewidth=2) +
  geom_hline(yintercept = 0, linetype ="dashed", color = "gray40") +
  theme_minimal() +
  scale_color_manual(values =setNames(colors, results$file))+
  labs(title = "Recall ISPS")+
  ylim(-0.003, .014)+
  theme(
    plot.title= element_text(size = 30, hjust = 0.5),
    plot.margin = unit(c(1,.5,.5,.5),"cm"),
    panel.grid.major.x = element_blank(),
    #panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    axis.title.y = element_text(size = 30),
    axis.title.x = element_blank(),
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black"),
    axis.text = element_text(size = 25),
    axis.text.x = element_text(angle=90,size = 18),
    legend.position = "none")+
    ylab("Model Estimate")

ggsave('recallISPS_topicSim_estimates_v6.png', width = 4.5,height = 6, units = "in", dpi = 300)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

